### 2013-09-08 doc/dissertation/document/chapters/conclusion/conclusion.tex
finished sna draft

%%---------------------------------------------------------------------------%%
\section{Parallel Monte Carlo Synthetic Acceleration Methods\ }
\label{sec:parallel_mc_conclusions}
A new parallel MCSA algorithm was developed for this work to meet the
goal of demonstrating the improved scalability on leadership-class
hardware. It was found the MCSA can indeed be effectively parallelized
using the multiple-set overlapping-domain decomposition algorithm
borrowed from the reactor physics community. Using a neutron diffusion
problem, the parallel algorithm was verified to produce the same
results as two production Krylov methods.

>>>>

%%---------------------------------------------------------------------------%%
\section{Parallel Monte Carlo Synthetic Acceleration Methods\ }
\label{sec:parallel_mc_conclusions}
A new parallel MCSA algorithm was developed for this work to meet the
goal of demonstrating the improved scalability on leadership-class
hardware. It was found that MCSA can indeed be effectively parallelized
using the multiple-set overlapping-domain decomposition algorithm
borrowed from the reactor physics community. Using a neutron diffusion
problem, the parallel algorithm was verified to produce the same
results as two production Krylov methods.

### 2013-09-08 doc/dissertation/document/chapters/parallel_mc/parallel_mc.tex
finished sna draft

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_strong_overlap_diff.pdf}
  \end{center}
  \caption{\textbf{Strong scaling absolute efficiency difference with
      respect to the 0 overlap base case.} \textit{Values of 1, 2, 3,
      and 5 levels of overlap are compared here with the absolute
      difference of the absolute efficiencies presented.}}
  \label{fig:titan_strong_overlap_diff}
\end{figure}

@@

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_weak_overlap_diff.pdf}
  \end{center}
  \caption{\textbf{Weak scaling absolute efficiency difference with
      respect to the 0 overlap base case.} \textit{Values of 1, 2, 3,
      and 5 levels of overlap are compared here with the absolute
      difference of the absolute efficiencies presented.}}
  \label{fig:titan_weak_overlap_diff}
\end{figure}

>>>>

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_strong_overlap_diff.pdf}
  \end{center}
  \caption{\textbf{Strong scaling absolute efficiency difference with
      respect to the 0 overlap base case.} \textit{Values of 1, 2, 3,
      and 5 levels of overlap are compared here with the difference of
      the absolute efficiencies presented.}}
  \label{fig:titan_strong_overlap_diff}
\end{figure}

@@

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_weak_overlap_diff.pdf}
  \end{center}
  \caption{\textbf{Weak scaling absolute efficiency difference with
      respect to the 0 overlap base case.} \textit{Values of 1, 2, 3,
      and 5 levels of overlap are compared here with the difference of
      the absolute efficiencies presented.}}
  \label{fig:titan_weak_overlap_diff}
\end{figure}
